\documentclass{article}
\title{CIS 22C Group Project\\Team 2 --- Test Plan}
\author{Remy Dinh}

\begin{document}

\maketitle{}
\begin{enumerate}
    \item{Add a new record to the database.}
        \begin{enumerate}
            \item{Select option 1}
            \item{Follow the prompts, and add a record that doesn't already exist in the database.}
            \item{Select option 3 (search) and follow prompts to prove that new record exists in hash table.}
            \item{Select option 5 (BST printout) and follow prompts to prove that new record exists in the BST.}
        \end{enumerate}
    \item{Delete a record from the database.}
        \begin{enumerate}
            \item{Select option 7 to show hash table metadata \textit{before} deletion.}
            \item{Select option 2, and input name of a record to be deleted from the database.}
            \item{Select option 2 again, and try to remove the item again.}
            \item{Select option 5 to verify removal from BST.}
            \item{Select option 3 and use it to verify removal from hash table.}
            \item{Select option 7 to show hash table metadata \textit{after} deletion.}
        \end{enumerate}
    \item{Insert a synonym into the database, to demonstrate collision resolution.}
        \begin{enumerate}
            \item{Select option 1, and add an item with a country name that's a corruption of another. Say "Romania" becomes "ainamoR" (due to ASCII case-sensitivity)}
            \item{Basically repeat the first test to prove that the synonym was successfully added to the database.}
        \end{enumerate}
    \item{[Required Easter Egg] Display team member names}
        \begin{enumerate}
            \item{Select hidden option 42. Voila!}
        \end{enumerate}
    \item{Demonstrate Binary Search Tree orders items correctly.}
        \begin{enumerate}
            \item{Select option 5. This prints out an in-order traversal of the langTree, which is a BST of the data sorted by the secondary key, \textit{recognized language.}}
            \item{Manually input and delete a few records, then reprint the tree to show that they are getting added and deleted from the BST properly.}
        \end{enumerate}
    \item{Binary Search Tree indented print-out.}
        \begin{enumerate}
            \item{Select hidden option 47. Voila!}
        \end{enumerate}
    \item{Demonstrate undo delete functionality.}
        \begin{enumerate}
            \item{Select option 8, and verify that the undo stack is empty.}
            \item{Select option 2, and remove Romania.}
            \item{Select option 3, and verify that Romania cannot be found in the name table.}
            \item{Select option 4, and verify that Moldova is the only country in the BST with Romanian as a recognized language.}
            \item{Select option 8, and repeat the above options to verify that Romania has been successfully restored to the database.}
        \end{enumerate}
    \item{Verify data write functionality \& UndoStack Wipe}
        \begin{enumerate}
            \item{Add a few items manually, and remove a few items manually}
            \item{Select option 6 to write the state of the database to an output file.}
            \item{Verify the state of the database output file. (I just realized it's supposed to be in hashTable order)}
            \item{Try undoing a delete after writing to the output file. It shouldn't work!}
        \end{enumerate}
\end{enumerate}

\end{document}
